---
title: "Esports: League of Legands"
author: "*Charlie Tran*"
date: "12/13/2020"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, echo=FALSE}
library(tidyverse)     # for data cleaning and plotting
library(lubridate)     # for date manipulation
library(ggthemes)      # for more themes (including theme_map())
library(gganimate)     # for adding animation layers to ggplots
library(gifski)        # for creating the gif (don't need to load this library every time,but need it installed)
library(transformr)    # for "tweening" (gganimate)
library(patchwork)     # for nicely combining ggplot2 graphs  
library(gt)            # for creating nice tables
```

```{r data, echo = FALSE}
GeneralEsportData <- read.csv("GeneralEsportData.csv")

HistoricalEsportData <- read.csv("HistoricalEsportData.csv")

high_diamond_ranked_10min <- read.csv("high_diamond_ranked_10min.csv")

twitchdata <- read.csv("twitchdata.csv")

pro_lol_champs <- read.csv("champion_stats.csv")

pro_lol_matches <- read.csv("matches2020.csv")
```

## The Growing Esports Industry

-briefly discuss the growing industry and the history and games associated with the industry
  - end with with introducing the recent competiiton of league of legends and the affeect of the pandemic
  
- use the heneral and historical esports data
  - probably a line graph where the dates can be utilized
```{r echo = FALSE}

```

## What is League of Legends?

- explain the orgins
- explain the game, map, and structure of the bases of the game
  - add pictures of the map and legendary players
  
## Professional League of Legends Esports

-use the data and explain its meaning
- use the high diamond ranked games data 
- use the pro matches to show the level and difference between diamond and pro player games

```{r echo = FALSE}

```

## Why is this game imapctful to Esports?

# DID YOU UNCOMMENT THE KNIT IN THE BEGINNING?