---
title: "Esports: League of Legends"
author: "*Charlie Tran*"
date: "12/18/2020"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---


```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

```{r libraries, echo=FALSE}
library(tidyverse)     # for data cleaning and plotting
library(lubridate)     # for date manipulation
library(ggthemes)      # for more themes (including theme_map())
library(gganimate)     # for adding animation layers to ggplots
library(gifski)        # for creating the gif (don't need to load this library every time,but need it installed)
library(transformr)    # for "tweening" (gganimate)
library(patchwork)     # for nicely combining ggplot2 graphs  
library(gt)            # for creating nice tables
library(stringr)       # for string conversions
```

```{r data, echo = FALSE}
GeneralEsportData <- read.csv("GeneralEsportData.csv")

HistoricalEsportData <- read.csv("HistoricalEsportData.csv") %>% 
  mutate(Date = dmy(Date)) %>% 
  mutate(year = year(Date))

high_diamond_ranked_10min <- read.csv("high_diamond_ranked_10min.csv")

twitchdata <- read.csv("twitchdata.csv")

pro_lol_champs <- read.csv("champion_stats.csv")

pro_lol_matches <- read.csv("matches2020.csv")
```

## The Growing Esports Industry

-briefly discuss the growing industry and the history and games associated with the industry
  - end with with introducing the recent competiiton of league of legends and the affeect of the pandemic
  
- use the general and historical esports data
  - probably a line graph where the dates can be utilized
  
-add images for: Space Invaders, twin galaxies,
  
The first competitive games started on arcade machines in the late 1970s with Space Invader and Twin Galaxies where the professional players strive to beat each other's record to become the world record holder. In the 1980s, more games were released that many of us know today like Pac-Man. A shift from arcades to gaming consoles occurred with the release of Nintendo systems. The new popularized way of gaming was becoming more accessible to the average consumer than ever before. As Nintendo continued to grow through the 1990s, the fast advancing computer technology became a new and different mode of gaming with personal computers. 
```{r echo = FALSE}
barlinegraph <- HistoricalEsportData %>% 
  group_by(year) %>% 
  summarise(sumEarnings = sum(Earnings)/1000000) 
  
  
growth_time <- ggplot(barlinegraph, aes(x = year,
             y = sumEarnings))+
  geom_col(color = "darkblue",
           fill = "white")+
  geom_line(color = "red",
            size = 1)+
  labs(title = "Esports Professional Matches Prize Earnings",
       subtitle = "(Millions of US Dollars)",
       x = "",
       y = "",
       caption = "Data from EsportsEarnings.com")+
  theme_minimal()

perspectivebar <- HistoricalEsportData %>% 
  mutate(era = ifelse(year >= 1998 & year <= 2017,
                      "1998 - 2017",
                      "2018 - 2020")) %>%
  group_by(era) %>%
  summarise(total_earnings = sum(Earnings)/1000000) %>% 
  ggplot(aes(x = era,
             y = total_earnings,
             fill = era))+
  geom_col()+
  labs(y = "",
       x = "",
       caption = "Created by Charlie Tran")+
  theme_minimal()+
  theme(legend.position = "none")

growth_time + perspectivebar 
```


## What is League of Legends?

- explain the orgins
- explain the game, map, and structure of the bases of the game
  - add pictures of the map and legendary players
  
## Professional League of Legends Esports

-use the data and explain its meaning
- use the high diamond ranked games data 
- use the pro matches to show the level and difference between diamond and pro player games

```{r echo = FALSE}

```

## Why is this game imapctful to Esports?

## DID YOU UNCOMMENT THE KNIT IN THE BEGINNING?